Fast gravitational wave parameter estimation without compromises

### 2023-07-21 src/tex/ms.tex
Add CPU time paragraph

To demonstrate the performance of our parameter estimation pipeline, we apply
it to two real LIGO-Virgo events: GW150914 and GW170817. We use the priors
shown in Table \ref{tab:parameters}, and take 4 s of data sampled at 2048 Hz
starting at 20 Hz for GW150914, and 128 s of data sampled at 4096 Hz starting
at 23 Hz for GW170817; strain data and PSDs for both events are fetched from
GWOSC \citep{GWOSC}. We use the same normalizing flow model as the
injection-recovery study. For our specific choice of sampler settings, we
produce ${\sim}$2500 and 3500 \emph{effective samples}\footnote{Effective
samples here refers to the number of independent samples, which is the total
number of generated samples divided by their correlation length; we compute the
effective sample size using \software{arviz}
\citep{arviz_2019}, \url{https://python.arviz.org/en/stable/api/generated/arviz.ess.html}.
} for GW150914 and GW170817 respectively. Running on an \textsc{Nvidia} A100
GPU, the wall time for both events is around 3 minutes. Most of this time is
spent on just-in-time (JIT) compilation of the code; the actual sampling time
is only ${\sim}40$ s. We pre-compute the reference waveform parameters used to
hetetrodyne the likelihood for the two events, which is omitted in the
wall-time calculation.

>>>>

To demonstrate the performance of our parameter estimation pipeline, we apply it
to two real LIGO-Virgo events: GW150914 and GW170817. We use the priors shown in
Table \ref{tab:parameters}, and take 4 s of data sampled at 2048 Hz starting at
20 Hz for GW150914, and 128 s of data sampled at 4096 Hz starting at 23 Hz for
GW170817; strain data and PSDs for both events are fetched from GWOSC
\citep{GWOSC}. We use the same normalizing flow model as the injection-recovery
study. For our specific choice of sampler settings, we produce ${\sim}$2500 and
3500 \emph{effective samples}\footnote{Effective samples here refers to the
number of independent samples, which is the total number of generated samples
divided by their correlation length; we compute the effective sample size using
\software{arviz} \citep{arviz_2019},
\url{https://python.arviz.org/en/stable/api/generated/arviz.ess.html}. } for
GW150914 and GW170817 respectively. \corr{Running on a node with an
\textsc{Nvidia} 80GB A100 GPU and 16 intel skylake CPUs} \footnote{Note that the
CPU time is hard to benchmark in \software{Jax} due to JIT compilation and
asynchronous dispatch. Overall, we find 4 CPUs to be sufficient for our use
case. We chose 16 because of the ease of use of the local cluster.}, the wall
time for both events is around 3 minutes. Most of this time is spent on
just-in-time (JIT) compilation of the code; the actual sampling time is only
${\sim}40$ s. We pre-compute the reference waveform parameters used to
hetetrodyne the likelihood for the two events, which is omitted in the wall-time
calculation.
